Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-26 analysis/paper/paper.Rmd
Add figure 4

@@

>>>>

The changes made for the 2016 experiment appear to have worked, increasing the incidence and decreased variability of sheath blight in the plots.

@@

```{r figure-4, fig.cap="Tiller sheath blight incidence per hill in the 2015 and 2016 experiments. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
ggplot(RAW_data, aes(x = WMGT, y = TShB_incidence)) +
  geom_boxplot(fill = NA) +
  theme(axis.text.x = element_text(size = 8,
                                   angle = 45,
                                   hjust = 1)) +
  xlab("Treatment") +
  ylab("Incidence per Hill") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_grid(. ~ YEAR) +
  theme(legend.position = "bottom")
```
